partial: An R Package for Creating Partial Dependence Plots

### 2016-08-11 manuscript/greenwell.tex
minor edits

Limited implementations of Friedman's PDPs are available in packages \CRANpkg{randomForest} \citep{randomForest-pkg} and \CRANpkg{gbm}, among others; these are limited in the sense that they only apply to the models fit using these packages. For example, the \code{partialPlot} function in \pkg{randomForest} only applies to objects of class \code{"randomForest"}. While the \pkg{randomForest} implementation will only allow for a single predictor, the \pkg{gbm} implementation can deal with any subset of the predictor space; however, these implementations only apply to models fit using the respective package. Partial dependence functions are not restricted to tree-based models; they can be applied to any supervised learning algorithm (e.g., neural networks). However, to our knowledge, there is no general package for constructing PDPs  in R (e.g., PDPs for a \dfn{conditional random forest} as implemented by the \code{cforest} function in the \CRANpkg{party} and \CRANpkg{partykit} packages; see \citet{party-pkg} and \citet{partykit-pkg}, respectively). The \CRANpkg{partial} \citep{partial-pkg} package tries to close this gap by offering a general framework for PDPs that can be applied to several types of fitted models.

>>>>

Limited implementations of Friedman's PDPs are available in packages \CRANpkg{randomForest} \citep{randomForest-pkg} and \CRANpkg{gbm}, among others; these are limited in the sense that they only apply to the models fit using these packages. For example, the \code{partialPlot} function in \pkg{randomForest} only applies to objects of class \code{"randomForest"}. While the \pkg{randomForest} implementation will only allow for a single predictor, the \pkg{gbm} implementation can deal with any subset of the predictor space. Partial dependence functions are not restricted to tree-based models; they can be applied to any supervised learning algorithm (e.g., multiple linear regression and neural networks). However, to our knowledge, there is no general package for constructing PDPs  in R (e.g., PDPs for a \dfn{conditional random forest} as implemented by the \code{cforest} function in the \CRANpkg{party} and \CRANpkg{partykit} packages; see \citet{party-pkg} and \citet{partykit-pkg}, respectively). The \CRANpkg{partial} \citep{partial-pkg} package tries to close this gap by offering a general framework for PDPs that can be applied to several types of fitted models.
